Air Quality Data - PM2.5 Components

### 2021-01-24 code/data-analysis/config-file-generator.Rmd
dataset and config files for residual, effect modification and brfss data processing for bufferzone size

@@

@@

@@

@@

```{r ses adj. model for Carbons}
dataname <- "ndi-carbon.csv"
expo <- carbon

for (i in seq(1,length(expo),1)){
  filenames <- c( tempfile())
  for( f in  filenames ){
    cat(config.ses, file=f)
    x <- readLines(f)
    y <- gsub("dataset", dataname, x)
    z <- gsub("exposure", expo[i], y)
    for (j in seq(1,length(cuz),1)){
      w <- gsub("outcome", cuz[j], z)
      cat(w, file=f, sep="\n")
      k=j+length(cuz)*(i-1)
      writeLines(w, here('config-files','carbon-ses', paste(k,'.txt', sep = "")))
    }
  }
  file.remove(f)
  }
```

@@

>>>>

```{r load packages}
library(tidyverse)
library(here)
```

@@

```{r List of PM Components Residuals}
pmcres <- c("PM_AS","PM_CA","PM_CL","PM_NA","PM_NI","PM_NO3",
            "PM_OC","PM_PB","PM_SI","PM_SO4","PM_V","PM_ZN")
```

```{r List of Factors Residuals}
facres <- c("PM_Factor1","PM_Factor2","PM_Factor3","PM_Factor4",
            "PM_Factor5","PM_Factor6","PM_Factor7","PM_Factor8")
```

@@

```{r List of PM Components Sub}
pmc.sub <- c("AS","CA","CL","NA","NI","NO3","OC",
             "PB","PM","SI","SO4","V","ZN")
```

```{r List of PM Components Yr Sub}
pmc.sub.yr <- c("Yr_AS","Yr_CA","Yr_CL","Yr_NA","Yr_NI","Yr_NO3","Yr_OC",
             "Yr_PB","Yr_PM","Yr_SI","Yr_SO4","Yr_V","Yr_ZN")
```

@@

```{r Config file - EM Models}
config.em <- c("# data path
data_path=/scratch/fatemehkp/projects/data/analysis/dataset

# loader settings
# separated symbol for the given data
sep=,
# the predictors are included in the model
predictors=Yr_exposure, subg, subg_exposure, ses
# stratas
stratas=StrID, SiteID
# death
death=no_death_outcome
# life
life=no_enrollee

```{r Config file - BRFSS Models}
config.brfss <- c("# data path
data_path=/scratch/fatemehkp/projects/data/analysis/dataset

# loader settings
# separated symbol for the given data
sep=,
# the predictors are included in the model
predictors=Yr_exposure, ses, BMI, Race, Smoke, Diabt, Asthma, Drink
# stratas
stratas=StrID, SiteID
# death
death=no_death_outcome
# life
life=no_enrollee

@@

@@

```{r ses adj. model for components residuals}
dataname <- "ndi-pmc-residual.csv"
expo <- pmcres

for (i in seq(1,length(expo),1)){
  filenames <- c( tempfile())
  for( f in  filenames ){
    cat(config.ses, file=f)
    x <- readLines(f)
    y <- gsub("dataset", dataname, x)
    z <- gsub("exposure", expo[i], y)
    for (j in seq(1,length(cuz),1)){
      w <- gsub("outcome", cuz[j], z)
      cat(w, file=f, sep="\n")
      k=j+length(cuz)*(i-1)
      writeLines(w, here('config-files','pmc-resid', paste(k,'.txt', sep = "")))
    }
  }
  file.remove(f)
  }
```

```{r ses adj. model for factors excluding EC Residual}
dataname <- "ndi-fac-ex-ec-residual.csv"
expo <- facres

for (i in seq(1,length(expo),1)){
  filenames <- c( tempfile())
  for( f in  filenames ){
    cat(config.ses, file=f)
    x <- readLines(f)
    y <- gsub("dataset", dataname, x)
    z <- gsub("exposure", expo[i], y)
    for (j in seq(1,length(cuz),1)){
      w <- gsub("outcome", cuz[j], z)
      cat(w, file=f, sep="\n")
      k=j+length(cuz)*(i-1)
      writeLines(w, here('config-files','fac-resid', paste(k,'.txt', sep = "")))
    }
  }
  file.remove(f)
  }
```

```{r ses adj. model for components - race Asian}
dataname <- "ndi-pmc-raceA.csv"
expo <- pmc.sub
subg <- "rA"

for (i in seq(1,length(expo),1)){
  filenames <- c( tempfile())
  for( f in  filenames ){
    cat(config.em, file=f)
    x <- readLines(f)
    y <- gsub("dataset", dataname, x)
    z <- gsub("exposure", expo[i], y)
    s <- gsub("subg", subg, z)
    for (j in seq(1,length(cuz),1)){
      w <- gsub("outcome", cuz[j], s)
      cat(w, file=f, sep="\n")
      k=j+length(cuz)*(i-1)
      writeLines(w, here('config-files','pmc-race-A', paste(k,'.txt', sep = "")))
    }
  }
  file.remove(f)
  }
```

```{r ses adj. model for components - race Black}
dataname <- "ndi-pmc-raceB.csv"
expo <- pmc.sub
subg <- "rB"

for (i in seq(1,length(expo),1)){
  filenames <- c( tempfile())
  for( f in  filenames ){
    cat(config.em, file=f)
    x <- readLines(f)
    y <- gsub("dataset", dataname, x)
    z <- gsub("exposure", expo[i], y)
    s <- gsub("subg", subg, z)
    for (j in seq(1,length(cuz),1)){
      w <- gsub("outcome", cuz[j], s)
      cat(w, file=f, sep="\n")
      k=j+length(cuz)*(i-1)
      writeLines(w, here('config-files','pmc-race-B', paste(k,'.txt', sep = "")))
    }
  }
  file.remove(f)
  }
```

```{r ses adj. model for components - race Hispanic}
dataname <- "ndi-pmc-raceH.csv"
expo <- pmc.sub
subg <- "rH"

for (i in seq(1,length(expo),1)){
  filenames <- c( tempfile())
  for( f in  filenames ){
    cat(config.em, file=f)
    x <- readLines(f)
    y <- gsub("dataset", dataname, x)
    z <- gsub("exposure", expo[i], y)
    s <- gsub("subg", subg, z)
    for (j in seq(1,length(cuz),1)){
      w <- gsub("outcome", cuz[j], s)
      cat(w, file=f, sep="\n")
      k=j+length(cuz)*(i-1)
      writeLines(w, here('config-files','pmc-race-H', paste(k,'.txt', sep = "")))
    }
  }
  file.remove(f)
  }
```

```{r ses adj. model for components - race White}
dataname <- "ndi-pmc-raceW.csv"
expo <- pmc.sub
subg <- "rW"

for (i in seq(1,length(expo),1)){
  filenames <- c( tempfile())
  for( f in  filenames ){
    cat(config.em, file=f)
    x <- readLines(f)
    y <- gsub("dataset", dataname, x)
    z <- gsub("exposure", expo[i], y)
    s <- gsub("subg", subg, z)
    for (j in seq(1,length(cuz),1)){
      w <- gsub("outcome", cuz[j], s)
      cat(w, file=f, sep="\n")
      k=j+length(cuz)*(i-1)
      writeLines(w, here('config-files','pmc-race-W', paste(k,'.txt', sep = "")))
    }
  }
  file.remove(f)
  }
```

```{r ses adj. model for factors - race Asian}
dataname <- "ndi-fac-raceA.csv"
expo <- fac
subg <- "rA"

for (i in seq(1,length(expo),1)){
  filenames <- c( tempfile())
  for( f in  filenames ){
    cat(config.em, file=f)
    x <- readLines(f)
    y <- gsub("dataset", dataname, x)
    z <- gsub("exposure", expo[i], y)
    s <- gsub("subg", subg, z)
    for (j in seq(1,length(cuz),1)){
      w <- gsub("outcome", cuz[j], s)
      cat(w, file=f, sep="\n")
      k=j+length(cuz)*(i-1)
      writeLines(w, here('config-files','fac-race-A', paste(k,'.txt', sep = "")))
    }
  }
  file.remove(f)
  }
```

```{r ses adj. model for factors - race Black}
dataname <- "ndi-fac-raceB.csv"
expo <- fac
subg <- "rB"

for (i in seq(1,length(expo),1)){
  filenames <- c( tempfile())
  for( f in  filenames ){
    cat(config.em, file=f)
    x <- readLines(f)
    y <- gsub("dataset", dataname, x)
    z <- gsub("exposure", expo[i], y)
    s <- gsub("subg", subg, z)
    for (j in seq(1,length(cuz),1)){
      w <- gsub("outcome", cuz[j], s)
      cat(w, file=f, sep="\n")
      k=j+length(cuz)*(i-1)
      writeLines(w, here('config-files','fac-race-B', paste(k,'.txt', sep = "")))
    }
  }
  file.remove(f)
  }
```

```{r ses adj. model for factors - race Hispanic}
dataname <- "ndi-fac-raceH.csv"
expo <- fac
subg <- "rH"

for (i in seq(1,length(expo),1)){
  filenames <- c( tempfile())
  for( f in  filenames ){
    cat(config.em, file=f)
    x <- readLines(f)
    y <- gsub("dataset", dataname, x)
    z <- gsub("exposure", expo[i], y)
    s <- gsub("subg", subg, z)
    for (j in seq(1,length(cuz),1)){
      w <- gsub("outcome", cuz[j], s)
      cat(w, file=f, sep="\n")
      k=j+length(cuz)*(i-1)
      writeLines(w, here('config-files','fac-race-H', paste(k,'.txt', sep = "")))
    }
  }
  file.remove(f)
  }
```

```{r ses adj. model for factors - race White}
dataname <- "ndi-fac-raceW.csv"
expo <- fac
subg <- "rW"

for (i in seq(1,length(expo),1)){
  filenames <- c( tempfile())
  for( f in  filenames ){
    cat(config.em, file=f)
    x <- readLines(f)
    y <- gsub("dataset", dataname, x)
    z <- gsub("exposure", expo[i], y)
    s <- gsub("subg", subg, z)
    for (j in seq(1,length(cuz),1)){
      w <- gsub("outcome", cuz[j], s)
      cat(w, file=f, sep="\n")
      k=j+length(cuz)*(i-1)
      writeLines(w, here('config-files','fac-race-W', paste(k,'.txt', sep = "")))
    }
  }
  file.remove(f)
  }
```

```{r ses adj. model for components - Urban}
dataname <- "ndi-pmc-urban.csv"
expo <- pmc.sub
subg <- "urb"

for (i in seq(1,length(expo),1)){
  filenames <- c( tempfile())
  for( f in  filenames ){
    cat(config.em, file=f)
    x <- readLines(f)
    y <- gsub("dataset", dataname, x)
    z <- gsub("exposure", expo[i], y)
    s <- gsub("subg", subg, z)
    for (j in seq(1,length(cuz),1)){
      w <- gsub("outcome", cuz[j], s)
      cat(w, file=f, sep="\n")
      k=j+length(cuz)*(i-1)
      writeLines(w, here('config-files','pmc-urban', paste(k,'.txt', sep = "")))
    }
  }
  file.remove(f)
  }
```

```{r ses adj. model for components - Rural}
dataname <- "ndi-pmc-rural.csv"
expo <- pmc.sub
subg <- "rur"

for (i in seq(1,length(expo),1)){
  filenames <- c( tempfile())
  for( f in  filenames ){
    cat(config.em, file=f)
    x <- readLines(f)
    y <- gsub("dataset", dataname, x)
    z <- gsub("exposure", expo[i], y)
    s <- gsub("subg", subg, z)
    for (j in seq(1,length(cuz),1)){
      w <- gsub("outcome", cuz[j], s)
      cat(w, file=f, sep="\n")
      k=j+length(cuz)*(i-1)
      writeLines(w, here('config-files','pmc-rural', paste(k,'.txt', sep = "")))
    }
  }
  file.remove(f)
  }
```

```{r ses adj. model for components - Urban ses Low}
dataname <- "ndi-pmc-urban-sesL.csv"
expo <- pmc.sub
subg <- "sesL"

for (i in seq(1,length(expo),1)){
  filenames <- c( tempfile())
  for( f in  filenames ){
    cat(config.em, file=f)
    x <- readLines(f)
    y <- gsub("dataset", dataname, x)
    z <- gsub("exposure", expo[i], y)
    s <- gsub("subg", subg, z)
    for (j in seq(1,length(cuz),1)){
      w <- gsub("outcome", cuz[j], s)
      cat(w, file=f, sep="\n")
      k=j+length(cuz)*(i-1)
      writeLines(w, here('config-files','pmc-urban-sesL', paste(k,'.txt', sep = "")))
    }
  }
  file.remove(f)
  }
```

```{r ses adj. model for components - Urban ses Middle}
dataname <- "ndi-pmc-urban-sesM.csv"
expo <- pmc.sub
subg <- "sesM"

for (i in seq(1,length(expo),1)){
  filenames <- c( tempfile())
  for( f in  filenames ){
    cat(config.em, file=f)
    x <- readLines(f)
    y <- gsub("dataset", dataname, x)
    z <- gsub("exposure", expo[i], y)
    s <- gsub("subg", subg, z)
    for (j in seq(1,length(cuz),1)){
      w <- gsub("outcome", cuz[j], s)
      cat(w, file=f, sep="\n")
      k=j+length(cuz)*(i-1)
      writeLines(w, here('config-files','pmc-urban-sesM', paste(k,'.txt', sep = "")))
    }
  }
  file.remove(f)
  }
```

```{r ses adj. model for components - Urban ses High}
dataname <- "ndi-pmc-urban-sesH.csv"
expo <- pmc.sub
subg <- "sesH"

for (i in seq(1,length(expo),1)){
  filenames <- c( tempfile())
  for( f in  filenames ){
    cat(config.em, file=f)
    x <- readLines(f)
    y <- gsub("dataset", dataname, x)
    z <- gsub("exposure", expo[i], y)
    s <- gsub("subg", subg, z)
    for (j in seq(1,length(cuz),1)){
      w <- gsub("outcome", cuz[j], s)
      cat(w, file=f, sep="\n")
      k=j+length(cuz)*(i-1)
      writeLines(w, here('config-files','pmc-urban-sesH', paste(k,'.txt', sep = "")))
    }
  }
  file.remove(f)
  }
```

```{r ses adj. model for components - West}
dataname <- "ndi-pmc-west.csv"
expo <- pmc.sub
subg <- "rW"

for (i in seq(1,length(expo),1)){
  filenames <- c( tempfile())
  for( f in  filenames ){
    cat(config.em, file=f)
    x <- readLines(f)
    y <- gsub("dataset", dataname, x)
    z <- gsub("exposure", expo[i], y)
    s <- gsub("subg", subg, z)
    for (j in seq(1,length(cuz),1)){
      w <- gsub("outcome", cuz[j], s)
      cat(w, file=f, sep="\n")
      k=j+length(cuz)*(i-1)
      writeLines(w, here('config-files','pmc-west', paste(k,'.txt', sep = "")))
    }
  }
  file.remove(f)
  }
```

```{r ses adj. model for components - Midwest}
dataname <- "ndi-pmc-midwest.csv"
expo <- pmc.sub
subg <- "rMW"

for (i in seq(1,length(expo),1)){
  filenames <- c( tempfile())
  for( f in  filenames ){
    cat(config.em, file=f)
    x <- readLines(f)
    y <- gsub("dataset", dataname, x)
    z <- gsub("exposure", expo[i], y)
    s <- gsub("subg", subg, z)
    for (j in seq(1,length(cuz),1)){
      w <- gsub("outcome", cuz[j], s)
      cat(w, file=f, sep="\n")
      k=j+length(cuz)*(i-1)
      writeLines(w, here('config-files','pmc-midwest', paste(k,'.txt', sep = "")))
    }
  }
  file.remove(f)
  }
```

```{r ses adj. model for components - South}
dataname <- "ndi-pmc-south.csv"
expo <- pmc.sub
subg <- "rS"

for (i in seq(1,length(expo),1)){
  filenames <- c( tempfile())
  for( f in  filenames ){
    cat(config.em, file=f)
    x <- readLines(f)
    y <- gsub("dataset", dataname, x)
    z <- gsub("exposure", expo[i], y)
    s <- gsub("subg", subg, z)
    for (j in seq(1,length(cuz),1)){
      w <- gsub("outcome", cuz[j], s)
      cat(w, file=f, sep="\n")
      k=j+length(cuz)*(i-1)
      writeLines(w, here('config-files','pmc-south', paste(k,'.txt', sep = "")))
    }
  }
  file.remove(f)
  }
```

```{r ses adj. model for components - Northeast}
dataname <- "ndi-pmc-northeast.csv"
expo <- pmc.sub
subg <- "rNE"

for (i in seq(1,length(expo),1)){
  filenames <- c( tempfile())
  for( f in  filenames ){
    cat(config.em, file=f)
    x <- readLines(f)
    y <- gsub("dataset", dataname, x)
    z <- gsub("exposure", expo[i], y)
    s <- gsub("subg", subg, z)
    for (j in seq(1,length(cuz),1)){
      w <- gsub("outcome", cuz[j], s)
      cat(w, file=f, sep="\n")
      k=j+length(cuz)*(i-1)
      writeLines(w, here('config-files','pmc-northeast', paste(k,'.txt', sep = "")))
    }
  }
  file.remove(f)
  }
```

```{r ses adj. model for components - Age LE75}
dataname <- "ndi-pmc-ageLE75.csv"
expo <- pmc.sub
subg <- "aLE75"

for (i in seq(1,length(expo),1)){
  filenames <- c( tempfile())
  for( f in  filenames ){
    cat(config.em, file=f)
    x <- readLines(f)
    y <- gsub("dataset", dataname, x)
    z <- gsub("exposure", expo[i], y)
    s <- gsub("subg", subg, z)
    for (j in seq(1,length(cuz),1)){
      w <- gsub("outcome", cuz[j], s)
      cat(w, file=f, sep="\n")
      k=j+length(cuz)*(i-1)
      writeLines(w, here('config-files','pmc-ageLE75', paste(k,'.txt', sep = "")))
    }
  }
  file.remove(f)
  }
```

```{r ses adj. model for components - Age M75}
dataname <- "ndi-pmc-ageM75.csv"
expo <- pmc.sub
subg <- "aM75"

for (i in seq(1,length(expo),1)){
  filenames <- c( tempfile())
  for( f in  filenames ){
    cat(config.em, file=f)
    x <- readLines(f)
    y <- gsub("dataset", dataname, x)
    z <- gsub("exposure", expo[i], y)
    s <- gsub("subg", subg, z)
    for (j in seq(1,length(cuz),1)){
      w <- gsub("outcome", cuz[j], s)
      cat(w, file=f, sep="\n")
      k=j+length(cuz)*(i-1)
      writeLines(w, here('config-files','pmc-ageM75', paste(k,'.txt', sep = "")))
    }
  }
  file.remove(f)
  }
```

```{r ses adj. model for components - Female}
dataname <- "ndi-pmc-sexF.csv"
expo <- pmc.sub
subg <- "sexF"

for (i in seq(1,length(expo),1)){
  filenames <- c( tempfile())
  for( f in  filenames ){
    cat(config.em, file=f)
    x <- readLines(f)
    y <- gsub("dataset", dataname, x)
    z <- gsub("exposure", expo[i], y)
    s <- gsub("subg", subg, z)
    for (j in seq(1,length(cuz),1)){
      w <- gsub("outcome", cuz[j], s)
      cat(w, file=f, sep="\n")
      k=j+length(cuz)*(i-1)
      writeLines(w, here('config-files','pmc-sexF', paste(k,'.txt', sep = "")))
    }
  }
  file.remove(f)
  }
```

```{r ses adj. model for components - Male}
dataname <- "ndi-pmc-sexM.csv"
expo <- pmc.sub
subg <- "sexM"

for (i in seq(1,length(expo),1)){
  filenames <- c( tempfile())
  for( f in  filenames ){
    cat(config.em, file=f)
    x <- readLines(f)
    y <- gsub("dataset", dataname, x)
    z <- gsub("exposure", expo[i], y)
    s <- gsub("subg", subg, z)
    for (j in seq(1,length(cuz),1)){
      w <- gsub("outcome", cuz[j], s)
      cat(w, file=f, sep="\n")
      k=j+length(cuz)*(i-1)
      writeLines(w, here('config-files','pmc-sexM', paste(k,'.txt', sep = "")))
    }
  }
  file.remove(f)
  }
```

```{r ses adj. model for components - sites with BRFSS data}
dataname <- "ndi-pmc-brfss.csv"
expo <- pmc.sub.yr

for (i in seq(1,length(expo),1)){
  filenames <- c( tempfile())
  for( f in  filenames ){
    cat(config.ses, file=f)
    x <- readLines(f)
    y <- gsub("dataset", dataname, x)
    z <- gsub("exposure", expo[i], y)
    for (j in seq(1,length(cuz),1)){
      w <- gsub("outcome", cuz[j], z)
      cat(w, file=f, sep="\n")
      k=j+length(cuz)*(i-1)
      writeLines(w, here('config-files','pmc-brfss-0', paste(k,'.txt', sep = "")))
    }
  }
  file.remove(f)
  }
```

```{r ses adj. model for components - adj. BRFSS data}
dataname <- "ndi-pmc-brfss.csv"
expo <- pmc.sub

for (i in seq(1,length(expo),1)){
  filenames <- c( tempfile())
  for( f in  filenames ){
    cat(config.brfss, file=f)
    x <- readLines(f)
    y <- gsub("dataset", dataname, x)
    z <- gsub("exposure", expo[i], y)
    for (j in seq(1,length(cuz),1)){
      w <- gsub("outcome", cuz[j], z)
      cat(w, file=f, sep="\n")
      k=j+length(cuz)*(i-1)
      writeLines(w, here('config-files','pmc-brfss', paste(k,'.txt', sep = "")))
    }
  }
  file.remove(f)
  }
```

### 2021-01-24 code/data-analysis/factor-analysis.Rmd
dataset and config files for residual, effect modification and brfss data processing for bufferzone size

>>>>

```{r residuals of PM vs. Factors}
dt.pm.daily <- dt.pmc.daily %>% 
  select(Site.ID, Date, PM)

dt.fac.ex.ec.residual <- dt.fac.daily.ex.ec %>% 
  merge(dt.pm.daily) %>% 
  group_by(Site.ID) %>% 
  nest() %>% 
  mutate(PM_Factor1 = map(map(data, ~lm(PM ~ Factor1, data = .)), residuals),
         PM_Factor2 = map(map(data, ~lm(PM ~ Factor2, data = .)), residuals),
         PM_Factor3 = map(map(data, ~lm(PM ~ Factor3, data = .)), residuals),
         PM_Factor4 = map(map(data, ~lm(PM ~ Factor4, data = .)), residuals),
         PM_Factor5 = map(map(data, ~lm(PM ~ Factor5, data = .)), residuals),
         PM_Factor6  = map(map(data, ~lm(PM ~ Factor6,  data = .)), residuals),
         PM_Factor7 = map(map(data, ~lm(PM ~ Factor7, data = .)), residuals),
         PM_Factor8 = map(map(data, ~lm(PM ~ Factor8, data = .)), residuals)
         ) %>% 
  unnest(c(data, PM_Factor1:PM_Factor8)) %>% 
  select(-(Factor1:Factor8), -PM)

save(dt.fac.ex.ec.residual, file = here('data', 'processed', 'fac-ex-ec-residual.RDa'))
```

```{r Smoothing Data & Caluculating 1-yr mvavg for each month}
dt.air <- dt.fac.ex.ec.residual %>% 
  pivot_longer(cols = PM_Factor1:PM_Factor8,
               names_to = "Parameter.Symbol",
               values_to = "Value") %>% 
  arrange(Site.ID, Parameter.Symbol, Date)

dt.fac.ex.ec.residual.1yr <- para.monthly %>% 
  mutate(Year = floor(Date -0.01),
         Month = round((Date - Year)*12)) %>% 
  select(-Date) %>% 
  pivot_wider(names_sort = T,
              names_from = c(Parameter.Symbol),
              values_from = c(para.1yr)) %>% 
  arrange(Site.ID, Year, Month)

save(dt.fac.ex.ec.residual.1yr, file = here('data', 'processed', 'fac-ex-ec-residual-1yr.RDa'))

```

### 2021-01-24 code/data-processors/air-data-processor.Rmd
dataset and config files for residual, effect modification and brfss data processing for bufferzone size

```{r Call Functions}
source(here('code','data-processors','epa-air-data-download-function.R'))
source(here('code','data-processors','air-data-processor-function.R'))
source(here('code','data-processors','air-data-smooth-mvavg-function.R'))
```

```{r load data}
dirUSSpatial <- 'C:\\Users\\fkazem01\\Box\\Projects\\USA Spatial\\data\\processed\\'
load(paste0(dirUSSpatial,'state-region.RDa'))
load(paste0(dirUSSpatial,'site-zip-closest-bz12.RDa'))
load(paste0(dirUSSpatial,'site-zip.RDa'))
```

@@

# daily PM value for each site based on closest zipcode value
dt.pm.daily <- read.csv(here('data','processed','pm_pmc_daily.csv')) %>% 
  transmute(Site.ID = Site_ID,
            Date = mdy(chardate),
            PM) %>% 
  arrange(Site.ID, Date)

@@

```{r Air quality data Process}
map(dt.pmc.pm.w, ~sum(is.na(.)))

@@

save(dt.pmc.1yr, file = here('data', 'processed', 'pmc-1yr.RDa'))
write.csv(dt.pmc.1yr, file = here('data', 'processed', 'pmc-1yr.csv'), row.names = F)

@@

@@

```{r}
dt.pmc.daily <- dt.pmc.site.ndi %>% 
  select(Site.ID) %>% 
  merge(dt.pmc.sel)

@@

```{r}
test <- dt.pmc.daily %>% 
  group_by(Site.ID) %>% 
  nest() %>% 
  mutate(model = map(data, ~lm(PM ~ AS, data = .)),
         resid = map(model, residuals)) %>% 
  unnest(data, resid)
#208037
test2 <- unlist(unlist(test$model))
test2 <- residuals(test$model[[3]])

d <- dt.pmc.daily %>% 
  filter(Site.ID == "01-073-0023")

model <- lm(data = d, PM ~AS)

residuals(model)

d <- data.frame(state=rep(c('NY', 'CA'), c(10, 10)),
                                 year=rep(1:10, 2),
                                 response=c(rnorm(10), rnorm(10)))

d %>% 
  group_by(state) %>% 
  nest() %>% 
  mutate(model = map(data, ~lm(response ~ year, data = .)))
```

>>>>

```{r Call Functions}
source(here('code','data-processors','epa-air-data-download-function.R'))
source(here('code','data-processors','air-data-processor-function.R'))
source(here('code','data-processors','air-data-smooth-mvavg-function.R'))
#source('air-data-smooth-mvavg-function.R') # for Cluster
```

```{r load data}
dirUSSpatial <- 'C:\\Users\\fkazem01\\Box\\Projects\\USA Spatial\\data\\processed\\'
load(paste0(dirUSSpatial,'state-region.RDa'))
load(paste0(dirUSSpatial,'site-zip.RDa'))
load(here('data','processed','aqs-sites.RDa'))
```

@@

# daily PM value for each site based on zipcodes in 12-mile value
dt.pm.daily <- read.csv(here('data','processed','pm_pmc_daily.csv')) %>% 
  transmute(Site.ID = Site_ID,
            Date = mdy(chardate),
            PM) %>% 
  arrange(Site.ID, Date)

@@

```{r Air quality data Process - eligible sites}
map(dt.pmc.pm.w, ~sum(is.na(.)))

@@

save(dt.pmc.1yr, file = here('data', 'processed', 'pmc-1yr.RDa'))

@@

summary(dt.pmc.site.ndi$Location.Setting) 
fix(dt.pmc.site.ndi) # changed blanks to 'RURAL'

@@

```{r - daily data for eligible sites}
dt.pmc.daily <- dt.pmc.site.ndi %>% 
  select(Site.ID) %>% 
  merge(dt.pmc.sel)

@@

```{r residuals of PM vs. Components}
dt.pmc.residual <- dt.pmc.daily %>% 
  group_by(Site.ID) %>% 
  nest() %>% 
  mutate(PM_AS = map(map(data, ~lm(PM ~ AS, data = .)), residuals),
         PM_CA = map(map(data, ~lm(PM ~ CA, data = .)), residuals),
         PM_CL = map(map(data, ~lm(PM ~ CL, data = .)), residuals),
         PM_CU = map(map(data, ~lm(PM ~ CU, data = .)), residuals),
         PM_FE = map(map(data, ~lm(PM ~ FE, data = .)), residuals),
         PM_K  = map(map(data, ~lm(PM ~ K,  data = .)), residuals),
         PM_MG = map(map(data, ~lm(PM ~ MG, data = .)), residuals),
         PM_MN = map(map(data, ~lm(PM ~ MN, data = .)), residuals),
         PM_NA = map(map(data, ~lm(PM ~ `NA`, data = .)), residuals),
         PM_NI = map(map(data, ~lm(PM ~ NI, data = .)), residuals),
         PM_NO3 = map(map(data, ~lm(PM ~ NO3, data = .)), residuals),
         PM_PB = map(map(data, ~lm(PM ~ PB, data = .)), residuals),
         PM_SE = map(map(data, ~lm(PM ~ SE, data = .)), residuals),
         PM_SI  = map(map(data, ~lm(PM ~ SI,  data = .)), residuals),
         PM_SO4 = map(map(data, ~lm(PM ~ SO4, data = .)), residuals),
         PM_V = map(map(data, ~lm(PM ~ V, data = .)), residuals),
         PM_ZN = map(map(data, ~lm(PM ~ ZN, data = .)), residuals),
         PM_EC  = map(map(data, ~lm(PM ~ EC,  data = .)), residuals),
         PM_OC = map(map(data, ~lm(PM ~ OC, data = .)), residuals)
         ) %>% 
  unnest(c(data, PM_AS:PM_OC)) %>% 
  select(-(AS:PM))

save(dt.pmc.residual, file = here('data', 'processed', 'pmc-residual.RDa'))
```

```{r Smoothing Data & Caluculating 1-yr mvavg for each month}
dt.air <- dt.pmc.residual %>% 
  pivot_longer(cols = PM_AS:PM_OC,
               names_to = "Parameter.Symbol",
               values_to = "Value") %>% 
  arrange(Site.ID, Parameter.Symbol, Date)

dt.pmc.residual.1yr <- para.monthly %>% 
  mutate(Year = floor(Date -0.01),
         Month = round((Date - Year)*12)) %>% 
  select(-Date) %>% 
  pivot_wider(names_sort = T,
              names_from = c(Parameter.Symbol),
              values_from = c(para.1yr)) %>% 
  arrange(Site.ID, Year, Month)

save(dt.pmc.residual.1yr, file = here('data', 'processed', 'pmc-residual-1yr.RDa'))
```
